Initial estuarine response to inorganic nutrient inputs from a legacy mining facility adjacent to Tampa Bay, Florida

### 2022-03-17 revision2/review_response.Rmd

     * __Response__: The Tampa Bay Coastal Ocean Model was previously tested for sea level and velocity field veracity under extreme conditions, e.g., Hurricane Irma [@Chen18] and under more regular variations in tide, wind and river forcing by @Zhu15 and @Chen19.  Model results closely followed observations over the time scale associated with tides, wind forcing and the longer term averaged net estuarine circulation.  It was with this backdrop that we felt justified in adding a tracer component to examine how the Piney Point effluent would spread throughout Tampa Bay.  Two additional tests were then performed.  The first was to demonstrate that the model faithfully conserved the amount of tracer.  Thus, we plotted what was known to be released and compared this with the integrated amount of tracer within the Tampa Bay Coastal Ocean model simulation.  Both were identical.  Next, we compared patterns of modeled tracer distribution with ocean color observations by satellite remote sensing.  Again, the agreements were very good.  In essence, if a model is known to faithfully reproduce the three-dimensional circulation features, then it should perform similarly in tracking a passive scalar because the scalar is transported and spread by the circulation.  A dedicated paper of the modeling work (including model/data comparisons) is still in preparation. More details will be reported in that paper.  Preliminary results were reported at recent conferences:

      Weisberg, R.H. (2022). Tampa Bay Coastal Ocean Model Applications, Abstract presented at the Bay Area Scientific Information Symposium, St. Petersburg, Florida, March 2022.

      Liu, Y., Weisberg, R.H., Zheng, L., Sun, Y., Chen, J. (2021), Nowcast/Forecast of the Tampa Bay, Piney Point Effluent Plume: A Rapid Response, Abstract (OS35B-1036) presented at AGU Fall Meeting, New Orleans, Louisiana, December 2021.

      Also note that we have included additional results in the text that describe satellite-based estimates of chlorophyll concentration.  The results were consistent with model simulation results in tracking the initial phytoplankon bloom at the point of discharge (see bottom of page 12, third paragraph of initial water quality results).
